---
title: "Marketing Dashboard"
---

This dashboard connects what I learned in **IBM3202** to my career interests in marketing, digital promotion, customer engagement, and business analytics.

The goal of this page is to show how marketing data can be **organize** into **clear visuals** that help businesses make **better decisions**.

This dashboard uses sample marketing data to represent the types of metrics I would track for a business

```{r}
#| label: setup
#| include: false
#| message: false
#| warning: false

library(tidyverse)

marketing_data <- tibble(
  Month = factor(c("Jan", "Feb", "Mar", "Apr", "May", "Jun"),
                 levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun")),
  Website_Visits = c(1200, 1380, 1490, 1650, 1810, 1950),
  Social_Engagement = c(220, 260, 310, 355, 410, 465),
  Leads = c(42, 49, 57, 61, 73, 82),
  Conversion_Rate = c(3.5, 3.6, 3.8, 3.7, 4.0, 4.2)
)

latest <- marketing_data |> 
  filter(Month == "Jun")
```

## Latest Month Summary

```{r}
#| echo: false
#| message: false
#| warning: false

latest
```

For the latest month, the dashboard shows:

-   **Website Visits:** `r latest$Website_Visits`
-   **Social Engagement:** `r latest$Social_Engagement`
-   **Leads:** `r latest$Leads`
-   **Conversion Rate:** `r latest$Conversion_Rate`%

These KPIs connect to marketing because they help measure awareness, engagement, customer interest, and action.

## Website Visits Over Time

Website visits help measure digital visibility. In marketing, this can show whether more people are discovering a business, campaign, or organization online.

```{r}
#| echo: false
#| message: false
#| warning: false

ggplot(marketing_data, aes(x = Month, y = Website_Visits, group = 1)) +
  geom_line(linewidth = 1.2, color = "#243447") +
  geom_point(size = 3, color = "#006b4f") +
  labs(
    title = "Website Visits by Month",
    x = "Month",
    y = "Website Visits"
  ) +
  theme_minimal()
```

## Social Media Engagement

Social media engagement is important because it shows whether content is connecting with an audience. Strong content can help increase attention, interest, and participation.

```{r}
#| echo: false
#| message: false
#| warning: false

ggplot(marketing_data, aes(x = Month, y = Social_Engagement)) +
  geom_col(fill = "#006b4f") +
  labs(
    title = "Social Media Engagement by Month",
    x = "Month",
    y = "Engagement"
  ) +
  theme_minimal()
```

## Leads Generated

Leads represent potential customers or people showing interest. For a business, leads could come from website visits, product inquiries, social media messages, or promotional campaigns.

```{r}
#| echo: false
#| message: false
#| warning: false

ggplot(marketing_data, aes(x = Month, y = Leads)) +
  geom_col(fill = "#b57f00") +
  labs(
    title = "Leads Generated by Month",
    x = "Month",
    y = "Leads"
  ) +
  theme_minimal()
```

## Conversion Rate

Conversion rate shows the percentage of users who take a valuable action. In marketing, this matters because it helps measure whether attention is turning into results.

```{r}
#| echo: false
#| message: false
#| warning: false

ggplot(marketing_data, aes(x = Month, y = Conversion_Rate, group = 1)) +
  geom_line(linewidth = 1.2, color = "#243447") +
  geom_point(size = 3, color = "#b57f00") +
  labs(
    title = "Conversion Rate by Month",
    x = "Month",
    y = "Conversion Rate (%)"
  ) +
  theme_minimal()
```

## Reflection

A strong marketing strategy should attract attention, communicate value, and produce measurable results. Through IBM3202, I learned how tools like Quarto, R, dashboards, and Google Analytics can be used to organize business information clearly and support smarter decisions based on evidence instead of guessing.

I can apply these skills to real marketing situations, such as promoting products, improving social media performance, increasing event engagement, and evaluating marketing campaigns.
